Supplementary Materials of Impact of IPTp Regimen on Pregnancy Outcomes

### 2025-05-03 products/manuscript/supplement/Supplementary-Material.qmd
update supp

# Machine learning & modeling
library(tidymodels)         # Modeling framework (recipes, parsnip, workflows, tune, yardstick, rsample)
library(themis)             # Class-imbalance sampling (e.g., SMOTE)
library(dials)              # Parameter tuning grids
library(ranger)             # Random forest engine
library(xgboost)            # Gradient boosting engine
library(generalhoslem)
library(ResourceSelection)
library(rms)
```

>>>>

# Machine learning & modeling
library(tidymodels)         # Modeling framework (recipes, parsnip, workflows, tune, yardstick, rsample)
library(themis)             # Class-imbalance sampling (e.g., SMOTE)
library(dials)              # Parameter tuning grids
library(ranger)             # Random forest engine
library(xgboost)            # Gradient boosting engine
library(generalhoslem)
library(ResourceSelection)
library(rms)
library(tinytex)
```
